Figures and tables for paper

### 2021-09-11 README.Rmd
De-packagify the project

1. Open the compendium as a project in RStudio (double click on `donorheuristics.proj`).
2. Build the compendium package by clicking on the "Install and Restart" button in RStudio's "Build" panel.

You should now be able to run `library(donorheuristics)` and reproduce all the findings in the paper (as well as the paper itself).

@@

- `/data`: Data goes here. ***Temporarily* not tracked with git.**
- `/analysis`: All analysis related files go here as standalone R Markdown files dedicated to specific tasks (like `01_clean-data.Rmd` and `02_analysis.Rmd`, etc.). The most current version of this analysis notebook is accessible online at <https://stats.andrewheiss.com/why-donors-donate/>.
- `/R`: Various project-specific R scripts and functions go here. These are built as part of the package and are accessible after loading `library(donorheuristics)`.
- `/manuscript`: The actual writing goes here. A separate Makefile here generates the output as HTML, PDF (through XeTeX), and Word. For now, that Makefile depends on a bunch of helper scripts that only live on Andrew Heiss's computer, so he's the only one that can build the actual paper. Eventually he'll move those scripts (into the `/manuscript/pandoc` folder) here so anyone can build it.

@@

    ```r
    library(tidyverse)
    library(donorheuristics)
    library(here)

>>>>

@@

- `/data`: Data goes here. ***Temporarily* not tracked with git.**
- `/analysis`: All analysis related files go here as standalone R Markdown files dedicated to specific tasks (like `01_clean-data.Rmd` and `02_analysis.Rmd`, etc.). The most current version of this analysis notebook is accessible online at <https://stats.andrewheiss.com/why-donors-donate/>.
- `/R`: Various project-specific R scripts and functions go here.
- `/manuscript`: The actual writing goes here. A separate Makefile here generates the output as HTML, PDF (through XeTeX), and Word. For now, that Makefile depends on a bunch of helper scripts that only live on Andrew Heiss's computer, so he's the only one that can build the actual paper. Eventually he'll move those scripts (into the `/manuscript/pandoc` folder) here so anyone can build it.

@@

    ```r
    library(tidyverse)
    library(here)

    # Load custom plot functions
    source(here("R", "graphics.R"))

### 2021-09-11 analysis/03_analysis.Rmd
De-packagify the project

```{r load-packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(donorheuristics)
library(rstan)
library(bayesplot)
library(tidybayes)
library(loo)
library(ggridges)
library(ggraph)
library(ggdag)
library(here)

>>>>

```{r load-packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(rstan)
library(bayesplot)
library(tidybayes)
library(loo)
library(ggridges)
library(ggraph)
library(ggdag)
library(here)

### 2021-09-11 analysis/04_figs-tables.Rmd
De-packagify the project

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(magrittr)
library(donorheuristics)
library(tidybayes)
library(broom)
# library(ggridges)
library(ggraph)
library(ggdag)
library(pander)
library(patchwork)
library(scales)
library(here)

>>>>

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(magrittr)
library(tidybayes)
library(broom)
# library(ggridges)
library(ggraph)
library(ggdag)
library(pander)
library(patchwork)
library(scales)
library(here)

# Load custom plot functions
source(here("R", "graphics.R"))
